Various examples of cdf plots

### 2017-01-03 analysis/plot_cdf_eg.Rmd
Fixed bugs in function get_cdf in plot_cdf_eg.Rmd.

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(magrittr)
library(ashr)
library(ggplot2)
library(dscr)
library(REBayes)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

@@

  if (df$method == "truth"){
    s    = dsc$scenarios[[df$scenario]]
    galt = s$args$g
    g    = normalmix(c(pi0,(1 - pi0) * mixprop(galt)),
                     c(0,comp_mean(galt)),
                     c(0,comp_sd(galt)))
  } else {
    if (grepl("mixfdr",df$method))
      temp$output = mixfdr2fitted.g(temp$output)
    g = temp$output$fitted.g
  }
  return(data.frame(x = x,y = as.numeric(mixcdf(g,x)),pi0 = pi0))
}

@@

```{r mean_cdf, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
plot_mean_cdf(1:100,PLOTMETHODS=c("ash.n","ash.u","ash.hu","truth"),pi0filter=TRUE)
```

@@

```{r egcdf-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
plot_mean_cdf(1,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"))
```

@@

```{r mean_cdf_nopen-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr",
                     "mixfdr.tnull")
colScale        <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
source("../R/set_plot_colors.R")
```

@@

```{r egcdf-reduce-with-npmle, dev='pdf',fig.height=4.5, fig.width=6, crop=TRUE}
run_nplme = function(SEED = 1,
                     PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                                       "big-normal","bimodal")) {
  df = data.frame(seed = NULL,scenario = NULL,method = NULL,x = NULL,
                  y = NULL,pi0 = NULL)
  for(SCENARIO in PLOTSCENARIOS) {
    temp = dscr::load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z    = REBayes::GLmix(temp$input$betahat)
    df = rbind(df,data.frame(seed=SEED,scenario=SCENARIO,method="NPMLE",x=z$x,y=cumsum(z$y)/sum(z$y),pi0=NA))
  }
  return(df)
}

plot_mean_cdf_with_npmle = function(SEED=1,PLOTMETHODS=c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
      PLOTSCENARIOS=c("spiky","near-normal","flat-top","skew","big-normal","bimodal"),pi0filter=FALSE,...){
  if(length(SEED)>1){stop("plot with npmle only implemented for a single seed")}
  PLOTNAMES=PLOTSCENARIOS
  #set up dataframe with cdf for all methods and all datasets
  df= expand.grid(seed=SEED,scenario=PLOTSCENARIOS, method=PLOTMETHODS,stringsAsFactors = FALSE)
  df.cdf=plyr::ddply(df,.(seed,scenario,method), get_cdf)

  df.cdf$scenario=factor(df.cdf$scenario,levels=PLOTSCENARIOS)
  levels(df.cdf$scenario)=PLOTNAMES

@@

  p=ggplot(df.cdf,aes(x=x,y=y,color=method),...) +  xlim(c(-4,4)) + colScale + geom_line(lwd=1.2,alpha=0.7)  + theme(legend.position = "bottom")
  return(p)
}

plot_mean_cdf_with_npmle(1,PLOTMETHODS=c("truth","ash.hu"),PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","big-normal","bimodal")) + facet_wrap(~ scenario, nrow=2)
```

>>>>

```{r chunk_options, include=FALSE}
library(plyr)
library(dplyr)
library(magrittr)
library(ashr)
library(ggplot2)
library(dscr)
library(REBayes)
library(ashr)
source("chunk-options.R")
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
source("../R/set_plot_colors.R")
```

@@

  if (df$method == "truth"){
    s    = dsc$scenarios[[df$scenario]]
    galt = s$args$g
    g    = normalmix(c(pi0,(1 - pi0) * mixprop(galt)),
                     c(0,comp_mean(galt)),
                     c(0,comp_sd(galt)))
  } else {
    if (grepl("mixfdr",df$method)) {
      temp$output$fitted_g = mixfdr2fitted.g(temp$output)$fitted.g
    }
    g = temp$output$fitted_g
  }
  return(data.frame(x = x,y = as.numeric(mixcdf(g,x)),pi0 = pi0))
}

@@

```{r mean_cdf, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n","ash.u","ash.hu","truth"),
              pi0filter = TRUE)
```

@@

```{r egcdf-reduce, fig.height=3, fig.width=6, crop=TRUE, dev='pdf'}
plot_mean_cdf(1,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"))
```

@@

```{r mean_cdf_nopen-reduce, fig.height=3, fig.width=6, crop=TRUE, dev='pdf'}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr",
                     "mixfdr.tnull")
colScale        <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
source("../R/set_plot_colors.R")
```

@@

TO DO (maybe): Add more details here about this chunk?

```{r egcdf-reduce-with-npmle, dev='pdf',fig.height=4.5, fig.width=6, crop=TRUE}
run_nplme = function(SEED = 1,
                     PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                                       "big-normal","bimodal")) {
  df = data.frame(seed = NULL,scenario = NULL,method = NULL,x = NULL,
                  y = NULL,pi0 = NULL)
  for(SCENARIO in PLOTSCENARIOS) {
    temp = load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z    = GLmix(temp$input$betahat)
    df = rbind(df,data.frame(seed = SEED,scenario = SCENARIO,method = "NPMLE",
                             x = z$x,y = cumsum(z$y)/sum(z$y),pi0 = NA))
  }
  return(df)
}

plot_mean_cdf_with_npmle = 
  function(SEED          = 1,
           PLOTMETHODS   = c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
           PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                             "big-normal","bimodal"),
           pi0filter     = FALSE,...) {
  if (length(SEED) > 1)
    stop("plot with npmle only implemented for a single seed")
  PLOTNAMES = PLOTSCENARIOS

  # Set up dataframe with cdf for all methods and all datasets.
  df = expand.grid(seed = SEED,scenario = PLOTSCENARIOS,method = PLOTMETHODS,
                   stringsAsFactors = FALSE)
  df.cdf = ddply(df,.(seed,scenario,method),get_cdf)

@@

  p = ggplot(df.cdf,aes(x = x,y = y,color = method),...) + 
    xlim(c(-4,4)) + colScale + geom_line(lwd = 1.2,alpha = 0.7) + 
    theme(legend.position = "bottom")
  return(p)
}

plot_mean_cdf_with_npmle(1,PLOTMETHODS = c("truth","ash.hu"),
                         PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                                           "big-normal","bimodal")) + 
  facet_wrap(~ scenario, nrow = 2)
```
